Data preparation for team category analysis

### 2023-05-31 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Completed team and supervisor characteristics section and saved

# CONTINUE FROM HERE

@@

Define `cohort_first` as `prep_xx`.

```{r}
cohort_first %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(
    across(
      .cols = c(-where(is.Date),
                -employee_e_mail_address,
                -position_category_code,
                -employee_name,
                -supervisor_display_name,
                -date_day_of_week,
                -position_number,
                -business_line_2_letter_department_id),
      .fns = list(dist = n_distinct,mode = getmode),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
  select(-person_id_mode,
         -business_line_2_letter_department_id_dist) %>% 
  # skim()
  glimpse()
```

```{r}
cohort_first %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(
    across(
      .cols = c(grade),
      .fns = list(min = min, max = max),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
  # select(-person_id_mode,
  #        -business_line_2_letter_department_id_dist) %>% 
  # skim()
  glimpse()
```

```{r}
# prep_xx <- 
  cohort_ids %>% 
  select(supervisor_e_mail_address) %>% 
  distinct() %>% 
  inner_join(
    cohort_panel %>% 
      filter(date >= date_cohort_month_start & date <= date_cohort_month_end),
    by = c("supervisor_e_mail_address" = "employee_e_mail_address")
  ) %>% 
  skim()
```

@@

All of these are null correlations, which will address in analysis.

@@

```{r}
prep_employees <- prep_building
```

@@

```{r}
save(prep_employees, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",
          glue::glue("prep_employees_{Sys.Date()}.rdata")))
```

>>>>

@@

Collect initial characteristics for supervisors for `check_in_panel` by joining `supervisor_e_mail_address` in `prep_building` to `employee_e_mail_address` and selecting for the first rows for each `supervisor_e_mail_address` by `date`.

```{r}
prep_a <-
  prep_building %>%
  select(supervisor_e_mail_address) %>%
  distinct() %>%
  inner_join(
    check_in_panel,
    by = c("supervisor_e_mail_address" = "employee_e_mail_address"),
    suffix = c("", "_of_supervisor")
  ) %>%
  arrange(supervisor_e_mail_address, date) %>%
  group_by(supervisor_e_mail_address) %>%
  summarise(across(.cols = everything(),
                   .fns = first)) %>%
  ungroup()
```

Review data

Create initial summary data of the team aggregating `cohort_first` by `supervisor_e_mail_address` and collecting the mode and distinct count for most variables.

```{r}
prep_b <-
  cohort_first %>%
  group_by(supervisor_e_mail_address) %>%
  summarise(across(
    .cols = c(
      -where(is.Date),-employee_e_mail_address,-position_category_code,-employee_name,-supervisor_display_name,-date_day_of_week,-position_number,-business_line_2_letter_department_id
    ),
    .fns = list(dist = n_distinct, mode = getmode),
    .names = "{.col}_{.fn}"
  )) %>%
  select(-person_id_mode) %>%
  ungroup()
```

Review data

Collect the minimum and maximum GS levels for the team by `supervisor_e_mail_address` from `cohort_first`.

```{r}
prep_c <-
  cohort_first %>%
  group_by(supervisor_e_mail_address) %>%
  summarise(across(
    .cols = c(grade),
    .fns = list(min = min, max = max),
    .names = "{.col}_{.fn}"
  )) %>%
  ungroup()
```

Review data

Create `prep_xx` by left joining the above to `supervisor_e_mail_address` in `prep_building`.

```{r}
prep_xx <-
  cohort_ids %>%
  select(supervisor_e_mail_address) %>%
  distinct() %>%
  left_join(prep_a) %>%
  left_join(prep_b) %>%
  left_join(prep_c)
```

@@

All of these are null from supervisors that didn't show up in the panel data.

@@

```{r}
prep_team <- prep_building
```

@@

```{r}
save(prep_team, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",
          glue::glue("prep_team_{Sys.Date()}.rdata")))
```
